A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-17 deprecated.tex
fix typos

\begin{abstract} 
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. For instance, smart meter data can assist in energy transition. Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location. Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers. Finally, we implement and evaluate the performance of the prototype.
\end{abstract}

@@

\subsection{choice of data storage}
We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible for data streams, and it is difficult to verify arbitrary data pieces, track data streams and categorize.

% may be removed
The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency. In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers. Broker is a centralized group that arrange the communication between the publishers and subscribers. However, the centralized architecture brings potential vulnerabilities and security issues:

@@

% move belows to background-archi
The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-effieciency. Connections of participants are built via brokers, which can avert sensitive information leaks in order to establish communication. Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities, for instance, the services are paralyzed if the server is crashed or attacked. Therefore, we adopted decentralized pub/sub model with no organization holding brokers. Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.

Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated. This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality. Also, the interactions among different actors are transparent and validable by automatically recording them on Ethereum Smart Contracts.

>>>>

\begin{abstract} 
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. For instance, smart meter data can assist in energy transition. Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location. Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers. Finally, we implement and evaluate the performance of the prototype.
\end{abstract}

@@

\subsection{choice of data storage}
We assume such storage system should be distributed which runs on the peer-to-peer network maintaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible for data streams, and it is difficult to verify arbitrary data pieces, track data streams and categorize.

% may be removed
The publish-subscribe messaging model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-efficiency. In the publish-subscribe system, a broker is the bridge to meet publishers and subscribers. Broker is a centralized group that arrange the communication between the publishers and subscribers. However, the centralized architecture brings potential vulnerabilities and security issues:

@@

% move belows to background-archi
The pub/sub model is widely used in IoT applications for exchanging data between devices due to its scalability and resource-efficiency. Connections of participants are built via brokers, which can avert sensitive information leaks in order to establish communication. Yet the existing pub/sub models\cite{MQTT, Looci, centralPubSub} mostly rely on centralized servers which may bring potential vulnerabilities, for instance, the services are paralyzed if the server is crashed or attacked. Therefore, we adopted decentralized pub/sub model with no organization holding brokers. Finally, \textbf{data providers}, \textbf{data consumers} and \textbf{brokers} are the three main roles in the data marketplace.

Ethereum Smart Contract is the key component to enforce the agreement between actors, such as data price and subscription period, and demands penalties when the rules are violated. This stimulates the economics incentives, and motivates data providers to involve data marketplace and maintain high data quality. Also, the interactions among different actors are transparent and validatable by automatically recording them on Ethereum Smart Contracts.
